### 2016-10-20 capability-machine.tex
Added lemmas from handwritten notes and fixed typos

                                                              \quad\text{$n_i = \rv_i$ or $n_i = \memreg{\rv_i}$}\\

@@

\subsection{Worlds}
Assume preordered \cofe{}\ $\Wor$ and isomorphism $\xi$ such that:
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]
We now define regions as
\[
\Regions \defeq (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments})))
\]
define region names to be natural numbers, i.e.,
\[
  \RegionNames \defeq \nats
\]
and define worlds as
\[
\Worlds \defeq \RegionNames \finparfun \Regions
\]
To define future worlds and regions, We use the ordering inherited from the preordered \cofes{}.
\begin{definition}[Future worlds]
  For $W, W' \in \Worlds$
 \begin{align*}
 W' \future W & & \text{ iff } & &
   \begin{gathered}
     \dom(W') \supseteq \dom(W)\\ 
     \text{ and } \\
     \forall r \in \dom(W) \ldotp W'(r) \future W(r)
   \end{gathered}
 \end{align*}
\end{definition}

@@

\begin{definition}[Heap satisfaction/erasure]
\begin{align*}
&\heapSat[\hs]{n}{W} \\
&\qquad\text{ iff }\\
&\exists R : \dom(W) \rightarrow \HeapSegments \ldotp & &\\
&\quad\begin{aligned}
  &\hs = \biguplus_{r \in \dom(W)} R(r) \\
  &\qquad\text{and}\\
  &\forall r \in \dom(W) \ldotp \forall n' < n \ldotp \npair[n']{R(r)} \in W(r).H(W(r).s)(\xi^{-1}(W))
\end{aligned} 
\end{align*}

@@

\subsubsection{Regiser-File Relation}
\label{subsubsec:register-file-relation}
This relation is used in the definition of the continuation relation as well as the expression relation.
\begin{align*}
  \stdrr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Regs} \\
  \stdrr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp
                     \begin{aligned}[t]
                       \{ \npair{\reg} \mid & \;\forall r \in \RegName \setminus \{\pcreg\} \ldotp \\
                                            & \;\quad  \npair{\reg(r)} \in \stdvr(W) \}
                     \end{aligned}
\end{align*}
Well-formedness lemmas for this definition:
\begin{lemma}[Register relation uniformity]
\label{lem:reg-dc}
  \begin{align*}
    &\forall \stdvr, n' < n \ldotp \forall W \ldotp \forall \reg \ldotp\\
    &\quad \npair{\reg} \in \stdrr(\stdvr)(W) \Rightarrow \npair[n']{\reg} \in \stdrr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

Well-definedness lemmas:
\begin{lemma}[Continuation relation uniformity]
\label{lem:stdkr-dc}
  \begin{align*}
    &\forall \stdvr \ldotp \forall n' < n \ldotp \forall W \ldotp \forall c \ldotp\\
    &\quad \npair{c} \in \stdkr(\stdvr)(W) \Rightarrow \npair[n']{c} \in \stdkr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

\subsubsection{Expression Relation}
\label{subsubsection:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' < n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}
\begin{lemma}[Expression relation non-expansive in world]
\label{lem:stder-ne-worlds}
\begin{align*}
  \forall \stdvr \ldotp \forall W_1 \nequal W_2 \ldotp \stder(\stdvr)(W_1) \nequal \stder(\stdvr)(W_2)
\end{align*}
\end{lemma}

@@

\begin{align*}
  \iota_{\var{start},\var{end}} & : \; (\Worlds \monnefun \UPred{\Words}) \nefun \Regions\\
  \iota_{\var{base},\var{end}} & \defeq \lambda \; \stdvr \ldotp ((\var{base},\var{end}),=,H_{\var{std}} (\stdvr)) \\ & \\
  H_{\var{std}} & : (\Worlds \monnefun \UPred{\Words}) \nefun \States \nefun \Worlds \monnefun \UPred{\HeapSegments} \\
  H_{\var{std}} \; \stdvr \; (\var{base},\var{end})\; W &  \defeq \left\{ \npair{\hs} \middle|
                                               \begin{aligned}
                                                 & \dom(\hs) = [\var{base},\var{end}] \land \\
                                                 & \forall \addr \in [\var{base},\var{end}] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi \; W)
                                               \end{aligned} \right\}
\end{align*}
As mentioned previously, the set of states contains the ``necessary'' states. For the above to make sense, the set of states contains pairs of natural numbers $(\var{base},\var{end})$.

@@

@@

\subsubsection{Capability Conditions}
\label{subsubsec:capability-conditions}
The definition of the value relation has the same conditions several times, so to define it consisely, we define the following conditions.
\begin{align*}
  \readCond{} & : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  \readCond{}(\stdvr)(\start,\addrend,W) & =        
  \begin{aligned}[t]
    \{ n \mid & \;\exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota_{\start',\addrend'}(\stdvr) \}
  \end{aligned}\\
 & \\
  \writeCond{} & : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  \writeCond{}(\stdvr)(\start,\addrend, W) & = 
  \begin{aligned}[t]
    \{ n \mid & \; \exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \; \qquad W(r) \nequal[n-1] \iota_{\start',\addrend'}(\stdvr)  \}
  \end{aligned}\\
 & \\
  \execCond{} & : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Perms \times \Worlds) \monnefun \DCPred{\nats} \\
  \execCond{}(\stdvr)(\start,\addrend,\perm,W) & = 
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
              & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned} \\
 & \\
  \entryCond{} & : \;  (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^3 \times \Worlds) \monnefun \DCPred{\nats} \\
  \entryCond{}(\stdvr)(\start,\addrend,\addr,W) & =
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned}
\end{align*}

@@

\begin{lemma}[Read condition monotone in world]
\label{lem:rc-mono-world}
  \begin{align*}
    &\forall \stdvr, n,W,W',\start, \addrend \ldotp \\
    &\quad  (\start,\addrend,W') \future (\start,\addrend,W) \\
    &\qquad \Rightarrow \readCond{}(\stdvr)(\start,\addrend,W') \supseteq \readCond{}(\stdvr)(\start,\addrend,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Read condition non-expansive in worlds]
\label{lem:rc-ne-world}
  \begin{align*}
    & \forall \stdvr, b,e, n, W, W' \ldotp \\
    & \quad (b,e,W) \nequal (b,e,W') \Rightarrow \\
    & \qquad \readCond{}(\stdvr)(b,e,W) \nequal \readCond{}(\stdvr)(b,e,W')\\
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Read-write condition monotone in world]
\label{lem:wc-mono-world}
  \begin{align*}
    &\forall \stdvr, n,W,W',\start, \addrend \ldotp \\
    &\quad  (\start,\addrend,W') \future (\start,\addrend,W) \\
    &\qquad \Rightarrow \writeCond{}(\stdvr)(\start,\addrend,W') \supseteq \writeCond{}(\stdvr)(\start,\addrend,W)
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Execute condition monotone in world]
\label{lem:ec-mono-world}
  \begin{align*}
    &\forall \stdvr,n,W, W',\start, \addrend, \perm \ldotp \\
    &\quad  (\start,\addrend,\perm,W') \future (\start,\addrend,\perm,W) \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(\start,\addrend,\perm,W') \supseteq \execCond{}(\stdvr)(\start,\addrend,\perm,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Execute condition non-expansive in worlds]
\label{lem:ec-ne-world}
  \begin{align*}
    &\forall \stdvr, W_1, W_2,n,\start,\addrend,\perm \ldotp \\
    &\quad (\start,\addrend,\perm,W_1) \nequal (\start,\addrend,\perm,W_2) \Rightarrow \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(b,e,p,W_1) \nequal \execCond{}(\stdvr)(b,e,p,W_2)
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Entry condition monotone in world]
  \label{lem:en-mono-world}
  \begin{align*}
    &\forall \stdvr,n,W, W',\start, \addrend, \addr \ldotp \\
    &\quad  (\start,\addrend,\addr,W') \future (\start,\addrend,\addr,W) \\
    &\qquad \Rightarrow \entryCond{}(\stdvr)(\start,\addrend,\perm,W') \supseteq \entryCond{}(\stdvr)(\start,\addrend,\perm,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Entry condition non-expansive in worlds]
\label{lem:en-ne-world}
  \begin{align*}
    &\forall \stdvr, W_1, W_2,n,\start,\addrend,\addr \ldotp \\
    &\quad (\start,\addrend,\perm,W_1) \nequal (\start,\addrend,\perm,W_2) \Rightarrow \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(b,e,p,W_1) \nequal \execCond{}(\stdvr)(b,e,p,W_2)
  \end{align*}
\end{lemma}
Finally, we need to show that all the conditions are non-expansive, but we later want to use Banach's fixed-point theorem to define the value relation. For this we will need that the above conditions are contractive, and if they are contractive, then they are also non-expansive, so we show that each of the conditions are contractive:
\begin{lemma}[Read condition contractive]
  \label{lem:rc-con}
  \begin{align*}
    &\forall \stdvr, \stdvr', n \ldotp \\
    &\quad \stdvr \nequal \stdvr' \Rightarrow \readCond{}(\stdvr) \nequal[n+1] \readCond{}(\stdvr')
  \end{align*}
\end{lemma}

@@

\subsubsection{Value Relation}
\label{subsubsec:value-relation}
The value relation, is defined as follows:
\begin{align*}
  \stdvr & :  (\Worlds \monnefun \UPred{Words}) \nefun \Worlds \monnefun \UPred{\Words} \\
  \stdvr &\defeq \lambda \; V \ldotp \lambda \; W \ldotp 
              \begin{aligned}[t]
  & \{ \npair{i} \mid i \in \ints \} 
    \union \\
         & \{ \npair{\stdcap[\noperm] }  \} 
           \union \\
         & \{ \npair{\stdcap[\readonly] } \mid n \in \readCond{}(V)(\start,\addrend,W) \} \union \\
         & \{ \npair{\stdcap[\readwrite] } \mid n \in \writeCond{}(V)(\start,\addrend,W) \} \union \\
         & \{ \npair{\stdcap[\exec]} \mid \\
         & \quad n \in \readCond{}(V)(\start,\addrend,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\exec,W) \}
           \union \\
           % For the entry case a capability is acceptable, if we can change it to an execute permission and put it as the pc and we otherwise have valid words in the registers, then the register file should be valid.
         & \{ \npair{\stdcap[\entry]} \mid n \in \entryCond{}(V)(\start,\addrend,\addr,W) \} \union \\
         & \{ \npair{\stdcap[\rwx]} \mid \\
         & \quad n \in \writeCond{}(V)(\start,\addrend,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\exec,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\rwx,W) \}
       \end{aligned}
\end{align*}
Using the Banach fixed-point theorem, we can find a fixed point for $\stdvr$ We will use this fixed point in the next section to define the logical relation we use in practice.

@@

\begin{lemma}[Heap satisfaction uniformity]
  \begin{align*}
    & \forall n,n',\heap, W \ldotp\\
    & \quad \heapSat{n}{W} \land n' < n \Rightarrow \heapSat{n'}{W}
  \end{align*}
\end{lemma}
\begin{proof}
  %TODO
\end{proof}

\begin{lemma}[Heap satisfaction non-expansive]
  \begin{align*}
    & \forall n,\heap, W, W' \ldotp\\
    & \quad \heapSat{n}{W} \land W \nequal W' \Rightarrow \heapSat{n}{W'}
  \end{align*}
\end{lemma}
\begin{proof}
  %TODO
\end{proof}

>>>>

                                                              \quad\text{$n_i = \rv_i$ or $n_i = \memreg(\rv_i)$}\\

@@

\subsection{Worlds}
Assume preordered \cofe{}\ $\Wor$ and isomorphism $\xi$ such that:
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]
$\xi$ is a morphism in the category $\CatP$ (the category of preordered \cofes{}), so it is non-expansive and monotone.

We now define regions as
\[
\Regions \defeq (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments})))
\]
define region names to be natural numbers, i.e.,
\[
  \RegionNames \defeq \nats
\]
and define worlds as
\[
\Worlds \defeq \RegionNames \finparfun \Regions
\]
To define future worlds and regions, We use the ordering inherited from the preordered \cofes{}.
\begin{definition}[Future worlds]
  For $W, W' \in \Worlds$
 \begin{align*}
 W' \future W & & \text{ iff } & &
   \begin{gathered}
     \dom(W') \supseteq \dom(W)\\ 
     \text{ and } \\
     \forall r \in \dom(W) \ldotp W'(r) \future W(r)
   \end{gathered}
 \end{align*}
\end{definition}

@@

\begin{definition}[Heap satisfaction/erasure]
\begin{align*}
&\heapSat[\hs]{n}{W} \\
&\qquad\text{ iff }\\
&\exists R : \dom(W) \rightarrow \HeapSegments \ldotp & &\\
&\quad\begin{aligned}
  &\hs = \biguplus_{r \in \dom(W)} R(r) \\
  &\qquad\text{and}\\
  &\forall r \in \dom(W) \ldotp \forall n' < n \ldotp \npair[n']{R(r)} \in W(r).H(W(r).s)(\xi^{-1}(W))
\end{aligned} 
\end{align*}
\end{definition}

\begin{lemma}[Heap satisfaction uniformity]
\label{lem:heapsat-dc}
  \begin{align*}
    & \forall n,n',\hs, W \ldotp\\
    & \quad \heapSat[\hs]{n}{W} \land n' \leq n \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

\begin{lemma}[Heap satisfaction non-expansive]
\label{lem:heapsat-ne}
  \begin{align*}
    & \forall n,\hs, W, W' \ldotp\\
    & \quad \heapSat[\hs]{n}{W} \land W \nequal W' \Rightarrow \heapSat[\hs]{n}{W'}
  \end{align*}
\end{lemma}

@@

\subsubsection{Regiser-File Relation}
\label{subsubsec:register-file-relation}
This relation is used in the definition of the continuation relation as well as the expression relation.
\begin{align*}
  \stdrr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Regs} \\
  \stdrr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp
                     \begin{aligned}[t]
                       \{ \npair{\reg} \mid & \;\forall r \in \RegName \setminus \{\pcreg\} \ldotp \\
                                            & \;\quad  \npair{\reg(r)} \in \stdvr(W) \}
                     \end{aligned}
\end{align*}
Well-formedness lemmas for this definition:
\begin{lemma}[Register relation uniformity]
\label{lem:reg-dc}
  \begin{align*}
    &\forall \stdvr, n' \leq n \ldotp \forall W \ldotp \forall \reg \ldotp\\
    &\quad \npair{\reg} \in \stdrr(\stdvr)(W) \Rightarrow \npair[n']{\reg} \in \stdrr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

Well-definedness lemmas:
\begin{lemma}[Continuation relation uniformity]
\label{lem:stdkr-dc}
  \begin{align*}
    &\forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall c \ldotp\\
    &\quad \npair{c} \in \stdkr(\stdvr)(W) \Rightarrow \npair[n']{c} \in \stdkr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

\subsubsection{Expression Relation}
\label{subsubsection:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}
\begin{lemma}[Expression relation non-expansive in world]
\label{lem:stder-ne-worlds}
\begin{align*}
  \forall \stdvr \ldotp \forall W_1 \nequal W_2 \ldotp \stder(\stdvr)(W_1) \nequal \stder(\stdvr)(W_2)
\end{align*}
\end{lemma}

@@

\begin{align*}
  \iota_{\var{start},\var{end}} & : \; (\Worlds \monnefun \UPred{\Words}) \nefun \Regions\\
  \iota_{\var{base},\var{end}} & \defeq \lambda \; \stdvr \ldotp ((\var{base},\var{end}),=,H_{\var{std}} (\stdvr)) \\ & \\
  H_{\var{std}} & : (\Worlds \monnefun \UPred{\Words}) \nefun \States \nefun \Wor \monnefun \UPred{\HeapSegments} \\
  H_{\var{std}} \; \stdvr \; (\var{base},\var{end})\; \hat{W} &  \defeq \left\{ \npair{\hs} \middle|
                                               \begin{aligned}
                                                 & \dom(\hs) = [\var{base},\var{end}] \land \\
                                                 & \forall \addr \in [\var{base},\var{end}] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi \; \hat{W})
                                               \end{aligned} \right\}
\end{align*}
As mentioned previously, the set of states contains the ``necessary'' states. For the above to make sense, the set of states contains pairs of natural numbers $(\var{base},\var{end})$.

@@

\begin{lemma}[$H_{\var{std}}$ is uniform]
  \label{lem:std-reg-dc}
  \begin{align*}
    & \forall \stdvr, s=(\start,\addrend), \hat{W}, n', n, \hs \ldotp \\
    & \quad n' \leq n \land \npair{\hs} \in H_{\var{std}} \; \stdvr \; s \; \hat{W} \\
    & \qquad \Rightarrow \npair[n']{\hs} \in H_{\var{std}} \; \stdvr \; s \; \hat{W}
  \end{align*}
\end{lemma}

\begin{lemma}[$H_{\var{std}}$ is non-expansive in state]
  \label{lem:std-reg-ne-state}
  \begin{align*}
    & \forall \stdvr, (\start,\addrend), (\start',\addrend'), n \ldotp \\
    & \quad  (\start,\addrend) \nequal (\start',\addrend') \\
    & \qquad \Rightarrow H_{\var{std}} \; \stdvr \; (\start,\addrend) \nequal H_{\var{std}} \; \stdvr \; (\start',\addrend')
  \end{align*}
\end{lemma}

@@

\subsubsection{Capability Conditions}
\label{subsubsec:capability-conditions}
The definition of the value relation has the same conditions several times, so to define it consisely, we define the following conditions.
\begin{align*}
  & \readCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \readCond{}(\stdvr)(\start,\addrend,W) =        
  \begin{aligned}[t]
    \{ n \mid & \;\exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota_{\start',\addrend'}(\stdvr) \}
  \end{aligned}\\
 & \\
  & \writeCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \writeCond{}(\stdvr)(\start,\addrend, W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \; \qquad W(r) \nequal[n-1] \iota_{\start',\addrend'}(\stdvr)  \}
  \end{aligned}\\
 & \\
  & \execCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Perms \times \Worlds) \monnefun \DCPred{\nats} \\
  & \execCond{}(\stdvr)(\start,\addrend,\perm,W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
              & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned} \\
 & \\
  & \entryCond{} : \;  (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^3 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \entryCond{}(\stdvr)(\start,\addrend,\addr,W) =
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned}
\end{align*}

@@

\begin{lemma}[Read condition monotone in world]
\label{lem:rc-mono-world}
  \begin{align*}
    &\forall \stdvr, n,W,W',\start, \addrend, \start',\addrend' \ldotp \\
    &\quad  (\start',\addrend',W') \future (\start,\addrend,W) \\
    &\qquad \Rightarrow \readCond{}(\stdvr)(\start',\addrend',W') \supseteq \readCond{}(\stdvr)(\start,\addrend,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Read condition non-expansive in worlds]
\label{lem:rc-ne-world}
  \begin{align*}
    & \forall \stdvr, \start, \addrend, \start', \addrend', n, W, W' \ldotp \\
    & \quad (\start, \addrend,W) \nequal (\start', \addrend',W') \Rightarrow \\
    & \qquad \readCond{}(\stdvr)(\start, \addrend,W) \nequal \readCond{}(\stdvr)(\start', \addrend',W')\\
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Read-write condition monotone in world]
\label{lem:wc-mono-world}
  \begin{align*}
    &\forall \stdvr,W,W',\start, \addrend, \start',\addrend' \ldotp \\
    &\quad  (\start',\addrend',W') \future (\start,\addrend,W) \\
    &\qquad \Rightarrow \writeCond{}(\stdvr)(\start',\addrend',W') \supseteq \writeCond{}(\stdvr)(\start,\addrend,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Read-write condition non-expansive in world]
  \label{lem:wc-ne-world}
  \begin{align*}
    &\forall \stdvr, n,W,W',\start, \addrend, \start',\addrend' \ldotp \\
    &\quad  (\start',\addrend',W') \nequal (\start,\addrend,W) \\
    &\qquad \Rightarrow \writeCond{}(\stdvr)(\start,\addrend,W) \nequal \writeCond{}(\stdvr)(\start',\addrend',W')
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Execute condition monotone in world]
\label{lem:ec-mono-world}
  \begin{align*}
    &\forall \stdvr,n,W, W',\start, \addrend, \perm,\start', \addrend', \perm' \ldotp \\
    &\quad  (\start',\addrend',\perm',W') \future (\start,\addrend,\perm,W) \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(\start',\addrend',\perm',W') \supseteq \execCond{}(\stdvr)(\start,\addrend,\perm,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Execute condition non-expansive in worlds]
\label{lem:ec-ne-world}
  \begin{align*}
    &\forall \stdvr, W, W',n,\start,\addrend,\perm,\start',\addrend',\perm' \ldotp \\
    &\quad (\start,\addrend,\perm,W) \nequal (\start',\addrend',\perm',W') \Rightarrow \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(\start,\addrend,\perm,W) \nequal \execCond{}(\stdvr)(\start',\addrend',\perm',W')
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Entry condition monotone in world]
  \label{lem:en-mono-world}
  \begin{align*}
    &\forall \stdvr,W, W',\start, \addrend, \addr, \start', \addrend', \addr' \ldotp \\
    &\quad  (\start',\addrend',\addr',W') \future (\start,\addrend,\addr,W) \\
    &\qquad \Rightarrow \entryCond{}(\stdvr)(\start',\addrend',\perm',W') \supseteq \entryCond{}(\stdvr)(\start,\addrend,\perm,W)
  \end{align*}
\end{lemma}

\begin{lemma}[Entry condition non-expansive in worlds]
\label{lem:en-ne-world}
  \begin{align*}
    &\forall \stdvr,n, W, W',\start,\addrend,\addr, \start', \addrend', \addr' \ldotp \\
    &\quad (\start,\addrend,\perm,W) \nequal (\start',\addrend',\perm',W') \Rightarrow \\
    &\qquad \Rightarrow \execCond{}(\stdvr)(\start,\addrend,\addr,W) \nequal \execCond{}(\stdvr)(\start',\addrend',\addr',W')
  \end{align*}
\end{lemma}
Finally, we need to show that all the conditions are non-expansive, but we later want to use Banach's fixed-point theorem to define the value relation. For this we will need that the above conditions are contractive, and if they are contractive, then they are also non-expansive, so we show that each of the conditions are contractive:
\begin{lemma}[Read condition contractive]
  \label{lem:rc-con}
  \begin{align*}
    &\forall \stdvr, \stdvr', n \ldotp \\
    &\quad \stdvr \nequal \stdvr' \Rightarrow \readCond{}(\stdvr) \nequal[n+1] \readCond{}(\stdvr')
  \end{align*}
\end{lemma}

@@

\subsubsection{Value Relation}
\label{subsubsec:value-relation}
The value relation, is defined as follows:
\begin{align*}
  \stdvr & :  (\Worlds \monnefun \UPred{Words}) \nefun \Worlds \monnefun \UPred{\Words} \\
  \stdvr &\defeq \lambda \; V \ldotp \lambda \; W \ldotp 
              \begin{aligned}[t]
  & \{ \npair{i} \mid i \in \ints \} 
    \union \\
         & \{ \npair{\stdcap[\noperm] }  \} 
           \union \\
         & \{ \npair{\stdcap[\readonly] } \mid n \in \readCond{}(V)(\start,\addrend,W) \} \union \\
         & \{ \npair{\stdcap[\readwrite] } \mid n \in \writeCond{}(V)(\start,\addrend,W) \} \union \\
         & \{ \npair{\stdcap[\exec]} \mid \\
         & \quad n \in \readCond{}(V)(\start,\addrend,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\exec,W) \}
           \union \\
           % For the entry case a capability is acceptable, if we can change it to an execute permission and put it as the pc and we otherwise have valid words in the registers, then the register file should be valid.
         & \{ \npair{\stdcap[\entry]} \mid n \in \entryCond{}(V)(\start,\addrend,\addr,W) \} \union \\
         & \{ \npair{\stdcap[\rwx]} \mid \\
         & \quad n \in \writeCond{}(V)(\start,\addrend,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\exec,W) \land \\
         & \quad n \in \execCond{}(V)(\start,\addrend,\rwx,W) \}
       \end{aligned}
\end{align*}

\begin{lemma}[Value relation uniformity]
  \begin{align*}
    & \forall V, W, n, n' \ldotp \\
    & \quad n' \leq n \land n \in \stdvr(V)(W) \\
    & \qquad \Rightarrow n' \in \stdvr(V)(W)
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation non-expansive in $V$]
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal \stdvr(V')
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation monotone in world]
  \begin{align*}
    & \forall V, W, W' \ldotp \\
    & W' \future W \Rightarrow \stdvr(V)(W') \supseteq \stdvr(V)(W)
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation non-expansive in world]
  \begin{align*}
    & \forall V, n, W, W' \ldotp \\
    & W \nequal W' \Rightarrow \stdvr(V)(W) \nequal \stdvr(V)(W')
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation contractive]
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal[n+1] \stdvr(V')
  \end{align*}
\end{lemma}

Using the Banach fixed-point theorem, we can find a fixed point for $\stdvr$ We will use this fixed point in the next section to define the logical relation we use in practice.

@@
